Learning words by recursive pragmatic reasoning about other agents: The blessing of social anxiety

### 2013-05-31 praglearn.tex
mini edit x
text edits

\section{Experiments: Pragmatic and word learning phenomena}

@@

\subsection{Horn implicature}
\label{sec:horn-implicature}

@@

% Mike's text:
% Such an implicature again arises naturally from our model. We create a situation in which expressions have differential costs (e.g. $[.5 1.0]$) and referents have differential probabilities (e.g. $[.8 .2]$). At the settings used throughout the manuscript, speakers in such a situation choose simple words to refer to common referents at different rates than for uncommon references. This situation breaks the symmetry though does not result in as dramatic a diagonal as in the specificity implicature, e.g. for the speaker, \footnote{Rows indicate words and columns indicate referents. For speakers, columns are normalized to indicate a distribution over words to be produced given referents, and for listeners rows are normalized to indicate a distribution on referents given words heard.}
% $\left[
%     \begin{array}{cc}
%       .88 & .54 \\
%       .12 & .46
%     \end{array} 
%   \right]$ 
% and for the listener,
% $\left[
%     \begin{array}{cc}
%       .77 & .23 \\
%       .65 & .35
%     \end{array} 
%   \right]$. See Section \ref{sec:hornlearn} for the consequences of repeating this implicature until it is lexicalized.

@@

Even very young children can learn words from individually ambiguous situations, e.g. where multiple words are spoken and multiple objects are present \cite{smith2008}. While no individual situation gives away the mapping, the pattern of co-occurrences between words and objects allows for learning. Our current model reproduces this pattern of results, converging to correct lexical mappings from ambiguous evidence. A representative simulation is shown in Fig. \ref{fig:cross-sit}.

\begin{SCfigure}[2.5]
  \includegraphics[width=0.2\textwidth]{figures/cross-sit-mod.pdf}
  \caption{Results from a simulation of cross-situational word learning. The posterior distribution over the learner's lexicon (diagonal entries are correct for word/object pairs 1 -- 3; word D is a distractor). Training data were situations including two of the three objects and a single word, either the distractor or a word matching one of the two objects. Crucially, at no point does the learner observe the meaning of any word; they observe only that a word was produced in each situation.}
  \label{fig:cross-sit}
\end{SCfigure}

@@

\section{Experiments 2: Lexical learning in pragmatic contexts}

XX maybe make the sections ``Pure pragmatics'' (scalar and horn implicature), ``Pure learning'' (cross-situational), ``Learning and pragmatics'' (subsection 1: disambiguation and learning scalar implicature, subsection 2: emergence with and without horn implicature)

>>>>

\section{Results: Pragmatic inference}

@@

\subsection{Horn implicature}

\label{sec:horn-implicature}

@@

@@

Even very young children can learn words from individually ambiguous situations, e.g. where multiple words are spoken and multiple objects are present \cite{smith2008}. While no individual situation gives away the mapping, the pattern of co-occurrences between words and objects allows for learning. Our current model reproduces this pattern of results, converging to correct lexical mappings from ambiguous evidence.

% A representative simulation is shown in Fig. \ref{fig:cross-sit}.

% \begin{SCfigure}[2.5]
%   \includegraphics[width=0.2\textwidth]{figures/cross-sit-mod.pdf}
%   \caption{Results from a simulation of cross-situational word learning. The posterior distribution over the learner's lexicon (diagonal entries are correct for word/object pairs 1 -- 3; word D is a distractor). Training data were situations including two of the three objects and a single word, either the distractor or a word matching one of the two objects. Crucially, at no point does the learner observe the meaning of any word; they observe only that a word was produced in each situation.}
%   \label{fig:cross-sit}
% \end{SCfigure}

\section{Results: Learning in pragmatic contexts}

@@

% XX maybe make the sections ``Pure pragmatics'' (scalar and horn implicature), ``Pure learning'' (cross-situational), ``Learning and pragmatics'' (subsection 1: disambiguation and learning scalar implicature, subsection 2: emergence with and without horn implicature)
